Simple Type Theory is not too Simple

### 2021-03-29 article.tex
Updates from Overleaf

@@

% snippet of code to be inserted for the subsection <Local Rings at Prime Ideals> up to the definition `one_local_ring_at`

@@

@@

@@

>>>>

\isacommand{interpretation}\isamarkupfalse%
\ rel{\isacharcolon}{\kern0pt}\ equivalence\ {\isachardoublequoteopen}R\ {\isasymtimes}\ S{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharbraceleft}{\kern0pt}{\isacharparenleft}{\kern0pt}x{\isacharcomma}{\kern0pt}y{\isacharparenright}{\kern0pt}\ {\isasymin}\ {\isacharparenleft}{\kern0pt}R{\isasymtimes}S{\isacharparenright}{\kern0pt}{\isasymtimes}{\isacharparenleft}{\kern0pt}R{\isasymtimes}S{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ x\ {\isasymsim}\ y{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\isanewline

@@

% snippet of code to be inserted for the subsection <Local Rings at Prime Ideals> up to the definition `one_local_ring_at`
\begin{isabelle}
\isacommand{context}\isamarkupfalse%
\ pr{\isacharunderscore}{\kern0pt}ideal\isanewline
\isakeyword{begin}\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ submonoid{\isacharunderscore}{\kern0pt}pr{\isacharunderscore}{\kern0pt}ideal{\isacharcolon}{\kern0pt}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}submonoid\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ I{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymone}{\isachardoublequoteclose}\isanewline
\isacommand{proof}\isamarkupfalse%
\isanewline
\ \ \isacommand{show}\isamarkupfalse%
\ {\isachardoublequoteopen}a\ {\isasymcdot}\ b\ {\isasymin}\ R{\isasymsetminus}I{\isachardoublequoteclose}\ \isakeyword{if}\ {\isachardoublequoteopen}a\ {\isasymin}\ R{\isasymsetminus}I{\isachardoublequoteclose}\ {\isachardoublequoteopen}b\ {\isasymin}\ R{\isasymsetminus}I{\isachardoublequoteclose}\ \isakeyword{for}\ a\ b\isanewline
\ \ \ \ \isacommand{using}\isamarkupfalse%
\ that\ \isacommand{by}\isamarkupfalse%
\ {\isacharparenleft}{\kern0pt}metis\ Diff{\isacharunderscore}{\kern0pt}iff\ absorbent\ comm{\isachardot}{\kern0pt}multiplicative{\isachardot}{\kern0pt}composition{\isacharunderscore}{\kern0pt}closed{\isacharparenright}{\kern0pt}\isanewline
\ \ \isacommand{show}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isasymone}\ {\isasymin}\ R{\isasymsetminus}I{\isachardoublequoteclose}\isanewline
\ \ \ \ \isacommand{using}\isamarkupfalse%
\ ideal{\isachardot}{\kern0pt}ideal{\isacharparenleft}{\kern0pt}{\isadigit{2}}{\isacharparenright}{\kern0pt}\ ideal{\isacharunderscore}{\kern0pt}axioms\ pr{\isacharunderscore}{\kern0pt}ideal{\isachardot}{\kern0pt}carrier{\isacharunderscore}{\kern0pt}neq\ pr{\isacharunderscore}{\kern0pt}ideal{\isacharunderscore}{\kern0pt}axioms\ \isanewline
\ \ \ \ \isacommand{by}\isamarkupfalse%
\ fastforce\isanewline
\isacommand{qed}\isamarkupfalse%
\ auto%
\isanewline
\isanewline
\isacommand{interpretation}\isamarkupfalse%
\ local{\isacharcolon}{\kern0pt}quotient{\isacharunderscore}{\kern0pt}ring\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ I{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ R\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\ {\isasymzero}\ {\isasymone}\isanewline
\ \ \isacommand{apply}\isamarkupfalse%
\ intro{\isacharunderscore}{\kern0pt}locales\isanewline
\ \ \isacommand{by}\isamarkupfalse%
\ {\isacharparenleft}{\kern0pt}meson\ submonoid{\isacharunderscore}{\kern0pt}def\ submonoid{\isacharunderscore}{\kern0pt}pr{\isacharunderscore}{\kern0pt}ideal{\isacharparenright}{\kern0pt}%
\ carrier{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ set{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}carrier{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ I{\isacharparenright}{\kern0pt}\isactrlsup {\isasyminverse}\ R\isactrlbsub {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlesub {\isachardoublequoteclose}\isanewline
\ add{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}add{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ local{\isachardot}{\kern0pt}add{\isacharunderscore}{\kern0pt}rel\ {\isachardoublequoteclose}\isanewline
\ mult{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}mult{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ local{\isachardot}{\kern0pt}mult{\isacharunderscore}{\kern0pt}rel\ {\isachardoublequoteclose}\isanewline
\ uminus{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}uminus{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ local{\isachardot}{\kern0pt}uminus{\isacharunderscore}{\kern0pt}rel\ {\isachardoublequoteclose}\isanewline
\ zero{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}zero{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ local{\isachardot}{\kern0pt}zero{\isacharunderscore}{\kern0pt}rel{\isachardoublequoteclose}\isanewline
\ one{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}one{\isacharunderscore}{\kern0pt}local{\isacharunderscore}{\kern0pt}ring{\isacharunderscore}{\kern0pt}at\ {\isasymequiv}\ local{\isachardot}{\kern0pt}one{\isacharunderscore}{\kern0pt}rel{\isachardoublequoteclose}\isanewline

@@

\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ \isanewline
\ \ \ \ is{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}frac{\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\isanewline
\ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}frac\ s\ V\ {\isasymequiv}\ {\isacharparenleft}{\kern0pt}{\isasymexists}r\ f{\isachardot}{\kern0pt}\ r\ {\isasymin}\ R\ {\isasymand}\ f\ {\isasymin}\ R\ {\isasymand}\ {\isacharparenleft}{\kern0pt}{\isasymforall}{\isasymqq}\ {\isasymin}\ V{\isachardot}{\kern0pt}\ \isanewline
\ \ \ \ \ \ \ \ \ \ \ \ f\ {\isasymnotin}\ {\isasymqq}\ {\isasymand}\ s\ {\isasymqq}\ {\isacharequal}{\kern0pt}\ quotient{\isacharunderscore}{\kern0pt}ring{\isachardot}{\kern0pt}frac\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ {\isasymqq}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ r\ f{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}regular\isanewline
\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}is{\isacharunderscore}{\kern0pt}regular\ s\ U\ {\isasymequiv}\ {\isasymforall}{\isasympp}{\isachardot}{\kern0pt}\ {\isasympp}\ {\isasymin}\ U\ {\isasymlongrightarrow}\ \isanewline
\ \ {\isacharparenleft}{\kern0pt}{\isasymexists}V{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ V\ {\isasymand}\ V\ {\isasymsubseteq}\ U\ {\isasymand}\ {\isasympp}\ {\isasymin}\ V\ {\isasymand}\ {\isacharparenleft}{\kern0pt}is{\isacharunderscore}{\kern0pt}locally{\isacharunderscore}{\kern0pt}frac\ s\ V{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymO}\ {\isacharunderscore}{\kern0pt}{\isachardoublequoteclose}\ {\isacharbrackleft}{\kern0pt}{\isadigit{9}}{\isadigit{0}}{\isacharbrackright}{\kern0pt}\ {\isadigit{9}}{\isadigit{0}}{\isacharparenright}{\kern0pt}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymO}\ U\ {\isasymequiv}\ {\isacharbraceleft}{\kern0pt}s{\isasymin}{\isacharparenleft}{\kern0pt}{\isasymPi}\isactrlsub E\ {\isasympp}{\isasymin}U{\isachardot}{\kern0pt}\ {\isacharparenleft}{\kern0pt}R\isactrlbsub {\isasympp}\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\isactrlesub {\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ is{\isacharunderscore}{\kern0pt}regular\ s\ U{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\isanewline
\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ \isanewline
\ \ \ \ \ \ \ \ \ \ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
\ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U\ s\ s{\isacharprime}{\kern0pt}\ {\isasymequiv}\ \isanewline
\ \ \ \ \ \ \ \ \ \ {\isasymlambda}{\isasympp}{\isasymin}U{\isachardot}{\kern0pt}\ quotient{\isacharunderscore}{\kern0pt}ring{\isachardot}{\kern0pt}add{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ {\isasympp}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isacharparenleft}{\kern0pt}s\ {\isasympp}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}s{\isacharprime}{\kern0pt}\ {\isasympp}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set{\isacharparenright}{\kern0pt}\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ \isanewline
\ \ \ \ \ \ \ \ \ \ \ \ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
\ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U\ s\ s{\isacharprime}{\kern0pt}\ {\isasymequiv}\ \isanewline
\ \ \ \ \ \ \ \ \ {\isasymlambda}{\isasympp}{\isasymin}U{\isachardot}{\kern0pt}\ quotient{\isacharunderscore}{\kern0pt}ring{\isachardot}{\kern0pt}mult{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ {\isasympp}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isacharparenleft}{\kern0pt}s\ {\isasympp}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}s{\isacharprime}{\kern0pt}\ {\isasympp}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
\ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U\ {\isasymequiv}\ \isanewline
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymlambda}{\isasympp}{\isasymin}U{\isachardot}{\kern0pt}\ quotient{\isacharunderscore}{\kern0pt}ring{\isachardot}{\kern0pt}zero{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ {\isasympp}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\isanewline
\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\isanewline
\ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
\ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ U\ {\isasymequiv}\ \isanewline
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymlambda}{\isasympp}{\isasymin}U{\isachardot}{\kern0pt}\ quotient{\isacharunderscore}{\kern0pt}ring{\isachardot}{\kern0pt}one{\isacharunderscore}{\kern0pt}rel\ {\isacharparenleft}{\kern0pt}R\ {\isasymsetminus}\ {\isasympp}{\isacharparenright}{\kern0pt}\ R\ {\isacharparenleft}{\kern0pt}{\isacharplus}{\kern0pt}{\isacharparenright}{\kern0pt}\ {\isacharparenleft}{\kern0pt}{\isasymcdot}{\isacharparenright}{\kern0pt}\ {\isasymzero}\ {\isasymone}{\isachardoublequoteclose}\isanewline
\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\isanewline
\ \ \ \ \ \ \ \ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}a\ set\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}\ \isanewline
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ set\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}a\ {\isasymtimes}\ {\isacharprime}{\kern0pt}a{\isacharparenright}{\kern0pt}\ set{\isacharparenright}{\kern0pt}{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
\ \ \ \ \ \ \ \ \isakeyword{where}\ {\isachardoublequoteopen}sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\ U\ V\ {\isasymequiv}\ {\isasymlambda}s{\isasymin}{\isacharparenleft}{\kern0pt}{\isasymO}\ U{\isacharparenright}{\kern0pt}{\isachardot}{\kern0pt}\ restrict\ s\ V{\isachardoublequoteclose}\isanewline
\ {\isacharparenleft}{\kern0pt}\isakeyword{in}\ comm{\isacharunderscore}{\kern0pt}ring{\isacharparenright}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}is{\isacharunderscore}{\kern0pt}sheaf{\isacharcolon}{\kern0pt}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings\ Spec\ is{\isacharunderscore}{\kern0pt}zariski{\isacharunderscore}{\kern0pt}open\ sheaf{\isacharunderscore}{\kern0pt}spec\ \isanewline
\ \ \ \ \ \ \ \ \ \ \ \ sheaf{\isacharunderscore}{\kern0pt}spec{\isacharunderscore}{\kern0pt}morphisms\ {\isasymO}b\ add{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ mult{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ \isanewline
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec\ one{\isacharunderscore}{\kern0pt}sheaf{\isacharunderscore}{\kern0pt}spec{\isachardoublequoteclose}

@@

\begin{isabelle}
\isacommand{locale}\isamarkupfalse%
\ ringed{\isacharunderscore}{\kern0pt}space\ {\isacharequal}{\kern0pt}\ sheaf{\isacharunderscore}{\kern0pt}of{\isacharunderscore}{\kern0pt}rings
\end{isabelle}

@@

\ morphism{\isacharunderscore}{\kern0pt}ringed{\isacharunderscore}{\kern0pt}spaces\ {\isacharequal}{\kern0pt}\isanewline
\ \ \ \ \ \ im{\isacharunderscore}{\kern0pt}sheaf\ X\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ {\isasymO}\isactrlsub X\ {\isasymrho}\isactrlsub X\ b\ add{\isacharunderscore}{\kern0pt}str\isactrlsub X\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub X\ zero{\isacharunderscore}{\kern0pt}str\isactrlsub X\ one{\isacharunderscore}{\kern0pt}str\isactrlsub X\ \isanewline
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ Y\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ f\ \isanewline
\ \ \ \ \ \ {\isacharplus}{\kern0pt}\ codom{\isacharcolon}{\kern0pt}\ ringed{\isacharunderscore}{\kern0pt}space\ Y\ is{\isacharunderscore}{\kern0pt}open\isactrlsub Y\ {\isasymO}\isactrlsub Y\ {\isasymrho}\isactrlsub Y\ d\ add{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ \isanewline
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ zero{\isacharunderscore}{\kern0pt}str\isactrlsub Y\ one{\isacharunderscore}{\kern0pt}str\isactrlsub Y\isanewline
\ \ \ \ \ \ \isakeyword{for}\ X\ \isakeyword{and}\ is{\isacharunderscore}{\kern0pt}open\isactrlsub X\ \isakeyword{and}\ {\isasymO}\isactrlsub X\ \isakeyword{and}\ {\isasymrho}\isactrlsub X\ \isakeyword{and}\ b\ \isakeyword{and}\ add{\isacharunderscore}{\kern0pt}str\isactrlsub X\ \isakeyword{and}\ mult{\isacharunderscore}{\kern0pt}str\isactrlsub X\isanewline
